Concurrent Programming with CXL

### 2020-05-17 book/paper.tex
Slight rewriting

However, mutual exclusion by itself easy to ensure.
For example, we could insert the following code to enter the
critical section:
\begin{code}
\begin{verbatim}
while True: pass;;
\end{verbatim}
\end{code}
This code will surely prevent two or more processes from being
at label \texttt{cs} at the same time.
But it does so by preventing \emph{any} process from reaching
the critical section.
The point is that we need another property besides mutual exclusion.

Mutual exclusion is an example of a \emph{safety property}, a
property that ensures that \emph{nothing bad will happen}, in this case
two processes being in the critical section. Now
we need a \emph{liveness property}: we want to ensure that
\emph{eventually something good will happen}.
There are various way of specifying this,
but here we will propose the following informally: when nobody is in the
critical section, then any process should be able to move forward and
enter the critical section.  We call this \emph{progress}.

>>>>

However, mutual exclusion by itself easy to ensure.
For example, we could insert the following code to enter the
critical section:
\begin{code}
\begin{verbatim}
while True: pass;;
\end{verbatim}
\end{code}
This code will surely prevent two or more processes from being
at label \texttt{cs} at the same time.
But it does so by preventing \emph{any} process from reaching
the critical section.
We clearly need another property besides mutual exclusion.

Mutual exclusion is an example of a \emph{safety property}, a
property that ensures that \emph{nothing bad will happen}, in this case
two processes being in the critical section.
What we need now a \emph{liveness property}: we want to ensure that
\emph{eventually something good will happen}.
There are various possible liveness properties we could use,
but here we will propose the following informally: when nobody is in the
critical section, then any process should be able to move forward and
enter the critical section.  We call this \emph{progress}.
